---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

body {
  background-color: #fff0f5;    
  color: #4b0033;                
  font-family: Georgia, serif;
  margin: 30px;
  text-align:center
}

h2 {
  color: #D60265;              
  padding-bottom: 5px;
  text-decoration:underline
}

```

## Ads seen whilst on social media

This report is based on observational data collected from my own social media scroll sessions over several days. Each time I opened Instagram or TikTok, I logged key details about what I saw. I recorded whether the first post was an ad or regular content, how many ads appeared during the session, what the ads were about, which platform I was using, whether the ads felt relevant to me, and how long the scroll session lasted. The purpose of collecting this data was to explore patterns in online advertising — including how frequently ads appear, what types of ads are most common, and how personalised or targeted they seem. 


```{r}
library(tidyverse)


logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vR6F7RwSGQIJ4_z8o1I_lDmgSY0OXXLRriy1z8NUka-mRN0jPE4P7aC3RGvcFru6V2sRU5dzZkuaV2E/pub?gid=1723247763&single=true&output=csv")

#PART D making summary values and plots

#rename all my varibles. 
latest_data <- logged_data %>%
  rename(
    first_seen = "Was the first post or story on your feed an ad or regular content?",
    number_ads = "How many ads did you see during this scroll session?",
    first_ad = "What was the first ad about?",
    majority = "What were majority of the ads about during this scroll session?",
    platform_used = "What platform were you using when you saw the ad?",
    ad_revelance ="Were these ads relevant to you?",
    length_scroll = "Approximately how long was the scroll session?"
  )
```
```{r}
#ADDING BAR CHARTS
ggplot (latest_data) +
  geom_bar(fill= "hotpink",
           aes(x=platform_used)) +
  labs(title = "Platform Used During Scroll Session",
       x = "Platform",
       y = "Frequency") +
  theme_minimal()

```
``` {r}
average <- mean(latest_data$number_ads, na.rm = TRUE) %>% round(1)

#comment
paste("On average, social media users saw", average, "ads per scroll session.")

```


```{r}
ggplot(latest_data, aes(x = majority)) + 
  geom_bar(fill = "pink") +
  labs(title = "Main Topics of Ads Seen on Social Media",
       x = "Ad Topic",
       y= "Count") +
  theme_minimal()


```

```{r}
#Second summary value( majority of the ads)
majority_of_ads <- names(which.max(table(latest_data$majority)))


#comment
paste("The most common type of ads during scroll sessions was", majority_of_ads, "which might reflect my browsing habits or interests. Seeing this pattern helped me understand the kinds of content that platforms are prioritising in my feed.")


```


```{r}
ggplot(latest_data, aes(x = factor(number_ads))) +
  geom_bar(fill = "deeppink") +
  labs(title = "How Many Ads Were Seen Per Scroll Session",
       x = "Number of Ads",
       y = "Frequency") +
  theme_minimal()


```

``` {r}
max_ads <- max(latest_data$number_ads, na.rm = TRUE)

paste("The highest number of ads I saw in a single scroll session was", max_ads,"which reflects the platform I tend to use the most. This pattern is important because it helps explain where the majority of ads in my dataset came from." )
```

